---
title: "Homework 01"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Homework 01
# Exercise 1

Null hypothese: (1)There is no relationship between TV and sales. (2)There is no relationship between radio and sales. (3)There is no relationship between newspaper and sales
Conclusions: based on the p-values, TV and radio are relatively significant variables for sales, while newspaper is not.

# Exercise 3
(a) iii is correct. The reason is as below:

Formula 1 - Staring salary for female = 85 + 10 *GPA + 0.07 *IQ + 0.01 * (GPA * IQ)
Formula 2 - Staring salary for male = 50 + 20 * GPA + 0.07 * IQ + 0.01 * (GPA * IQ)

While the coefficient of GPA is higher in Formula 2 than in Formula 1, the intercept in Formula 1 is higher than in Formula 2. Therefore, only when the GPA is high enough, males earn more on average than females.

(b) Put IQ=110 and a GPA=4.0 in to Formula 1, then the answer is 137.1.

(c) We should use p-value to decide wheatehr the effect is signicficant or not, other than using the value of coefficient. In addition, even though the coefficient is small, if GPA*IQ is very large, the effect is still significant.

# Exercise 4
(a) The RSS of cubic regression will be smaller because the cubic regression model is larger and can fit the traning data better.

(b) The RSS of cubic regression will be larger because the true realationship between X and Y is linear.

(c) The RSS of cubic regression will be smaller because a larger model will fit better in terms of traning data.

(d) Becase we don't know the true relation between X and Y, so we can't tell which RSS is larger.


# Exercise 5
(a) 
$$\hat{y}_i = x_i{\frac{\sum^n_{j=1}x_jy_j}{\sum^n_{k=1}{x_k}^2}} = \sum^n_{j=1}\frac{x_iy_j}{\sum^n_{k=1}{x_k}^2}y_j = \sum^n_{j=1}a_jy_j$$
so
$$a_j = \frac{x_iy_j}{\sum^n_{k=1}{x_k}^2}$$

# Exercise 6
According to (3.4), the least square line equation is $y = \hat{\beta_0} + \hat{\beta_1}x$, when \[x = \bar{x}\] we can get this formula:
\[y = \hat{\beta_0} + \hat{\beta_1}\bar{x} = \bar{y} - \hat{\beta_1}\bar{x} + \hat{\beta_1}\bar{x} = \bar{y}\]


# Exercise 7
assume \[\bar{x} = \bar{y} = 0\]
Then \[R^2 = 1 - \frac{RSS}{TSS} = 1 - \frac{\sum_i{(y_i - \hat{y}_i)}^2}{\sum_j{y_j}^2}\]  

According to \[\bar{y} = \beta_0 + \beta_1\bar{x} \], when \[\bar{x} = \bar{y} = 0\], then we have \[\beta_0 = 0\]  

So the formula becomes like this : \[\hat{y}_i = \hat{\beta_1}\hat{x}_i \]  

Then we can subsitute \[\hat{y}_i\] in $R^2$ with \[\frac{\sum^n_{j=1}x_jy_j}{\sum^n_{j=1}{x_j}^2}\] according to Question 5

So we get: \[R^2 = 1 - \frac{\sum_i(y_i - \sum_jx_jy_j/\sum_j{x_j}^2x_i)^2}{\sum_j{y_j}^2} = 1 - \frac{\sum_i{y_i}^2 - 2\sum_iy_i(\sum_jx_jy_j/\sum_j{x_j}^2)x_i + \sum_i(\sum_jx_jy_j/\sum_j{x_j}^2)^2{x_i}^2}{\sum_j{y_j}^2}\]
Then we get: 
\[R^2 = \frac{\sum_j{y_j}^2 - (\sum_i{y_i}^2 - 2\sum_iy_i(\sum_jx_jy_j/\sum_j{x_j}^2)x_i + \sum_i(\sum_jx_jy_j/\sum_j{x_j}^2)^2{x_i}^2)}{\sum_j{y_j}^2}\]
after calculation: 
\[R^2 = \frac{2(\sum_ix_iy_i)^2/\sum_j{x_j}^2 - (\sum_ix_iy_i)^2/\sum_j{x_j}^2}{\sum_j{y_j}^2} = \frac{(\sum_ix_iy_i)^2}{\sum_j{x_j}^2\sum_j{y_j}^2} = Cor(X,Y)^2\]

# Exercise 8
```{r}
library(ISLR)
attach(Auto)
lm.fit = lm(mpg ~ horsepower, data = Auto)
summary(lm.fit)
```
i) Yes, there is. The p-value of the F-statistic is less than 2.2e-16.

ii) The $R^2$ is 0.6059, so 60.59% of the variation in mpg can be explained by horsepower.

iii) Negative.

iv) 
```{r}
predict(lm.fit, data.frame(horsepower = 98), interval = 'confidence')
predict(lm.fit, data.frame(horsepower = 98), interval = 'prediction')
```
The predicted mpg is 24.46708.  The CI is between 23.97308 and 24.96108. The PI is between 14.8094 and 34.12476. 


(b)

```{r}
plot(Auto$horsepower,Auto$mpg, xlab = 'horsepower', ylab = 'mpg')
abline(lm.fit, col = 'red')
```


(c)

```{r}
par(mfrow = c(2,2))
plot(lm.fit)
```

# Exercise 9
(a)

```{r}
pairs(Auto)
```

(b)

```{r}
library(dplyr)
Auto %>% select(-name) %>% cor()
```

(c)

```{r}
lm.fitall = lm(mpg~.-name, data = Auto)
summary(lm.fitall)
```
i) Yes, there is because the p-value is very small.
ii) Displacement, weight, year, and origin have a statistically significant relationship with mpg.
iii) The coefficient for the year variable suggests that when other predictors remain the same, mpg will increase 0.75 when the year variable increases 1 unit.

(d)

```{r}
par(mfrow = c(2,2))
plot(lm.fitall)
```

There are outliers bigger than 2 or smaller than -2. There are also high leverage points like point 14.

(e)
```{r}
lim.fitall2 = lm(mpg~cylinders*displacement + displacement*weight, data = Auto)
summary(lim.fitall2)
```

 It's significant because the p-value is very small.
 
 
(f)

```{r}
par(mfrow = c(2, 2))
plot(log(Auto$weight), Auto$mpg)
plot(sqrt(Auto$weight), Auto$mpg)
plot((Auto$weight)^2, Auto$mpg)
```

Based on the graph, we can tell that only the log transformation is similar to linear relationship. Other transformations show the presence of non-linear relationships.

# Exercise 10
(a)
```{r}
carseatsfit = lm(Sales ~ Price + Urban + US, data = Carseats)
summary(carseatsfit)
```

(c)
$$Sales = 13.043469 -0.054459 \times Price -0.021916 \times Urban + 1.200573 \times US + ε$$
(d)
Price and US predictors.

(e)
```{r}
lm.car = lm(Sales ~ Price + US, data = Carseats)
summary(lm.car)
```

(f)
The $R^2$ for both model is 0.2393 which means that 23.93% of the variation is explained by the model.

(g)

```{r}
confint(lm.car)
```

(h)

```{r}
par(mfrow = c(2, 2))
plot(lm.car)
```

